Criticisms of the IHME COVID-19 model

### 2020-07-18 text/20/ihme-covid-model.Rmd
Reconcile, part 2

@@

+ This article was written before the COVID=19 pandemic. It provides a nice review of how SEIR models work and applies them to a variety of pandemics.

@@

>>>>

Robinson D. David's COVID Numbers. Available in [html format](https://davidscovidnumbers.wordpress.com/).

+ This blog post talks about COVID-19 in general terms with an emphasis on predictions for Minnesota and Stearns County. It tries to explain the meaning behind the many numbers that appear in various models.

@@

+ This article was written before the COVID-19 pandemic. It provides a nice review of how SEIR models work and applies them to a variety of pandemics.

@@

### Alternative prediction models

There are many prediction models out there and each one seems to take a different approach. I'm just getting started but I want to provide a brief summary of some of these models.

#### Imperial College of London

[US Predictions](https://mrc-ide.github.io/covid19usa/#/)

#### Iowa State
